---
title: "popularity and loneliness Study 2b Data Analysis"
output: html_notebook
---

We use groundhog (https://groundhogr.com/) to manage our packages. Groundhog makes sure that our package versions are consistent with the current date. This way, everyone will be using packages from the same date to prevent any issues related to package versioning in future analyses. 

To use groundhog, please: 
(1) make sure that you have the latest version of R/ RStudio installed; 
(2) install RTools
(3) make sure you are in a new R Session


The R Version used to create this file is: `R version 4.3.0 (2023-04-21 ucrt)`. You can change this out with your own version of R if you are using this template to create your own analysis. If you are reproducing another person's analysis, please download the version of R used by the previous person to ensure a proper reproduction of the code.

You can identify your version of R by typing `version` into the R Console

You can switch your R version by pressing `Tools` > `Global Options` > `R Version`


```{r download packages and format csv to prepare for analysis}

# if you need to install groundhog
#if(!suppressWarnings(require(groundhog))){remotes::install_github('CredibilityLab/groundhog')}

#call groundhog
library("groundhog")



# put all packages in and call groundhog
pkgs <- c('Rmisc', 'corrplot', 'tidyverse', 'broom.mixed', 'knitr', 'lmerTest', 'Hmisc', 'psych', 'simr', 'future', 'glue', 'sjmisc', 'quanteda', 'wordcloud', 'car', 'DeclareDesign', 'tidytext', 'mediation', 'hrbrthemes', 'MuMIn'
    )

pkgs_all <- c(pkgs)

# call groundhog. Change out the date for today's date (unless you are running an old analysis)
groundhog.library(pkgs_all, "2025-04-09")

#load data
input_dir = "../data/raw/data/"
output_dir = "../data/raw/anonymized-data/"
# df_trial <- read_rds("anonymized-data/df_trial.rds")
df_trial <- read_rds("../data/raw/anonymized-data/df_trial_w_agent_profiles.rds")
nrow(df_trial)/30
d <- read.csv("../data/raw/anonymized-data/df_agent.csv")
all_agents <- read_csv("../data/raw/anonymized-data/all_agents.csv")
qualtrics <- read.csv("../data/raw/anonymized-data/qtrcs_popularity_production.csv")

#modify variables
d$kept = factor(d$kept, labels =c ("eliminated", "kept"))
d$photo_nice = factor(d$photo_nice, labels = c("negative rating", "positive rating"))
d$absDif = abs (d$subject_rating-d$agent_rating)
d$trial = as.numeric(d$trial)
df_trial$trial=as.numeric(df_trial$trial)
d$dif = d$subject_rating-d$agent_rating
d$lonely_cat=factor(d$lonely_cat)
d$lonely_cat=relevel(d$lonely_cat,"low in loneliness")
d$.loneliness = 5-d$.loneliness


#functions
tidy. <- function(df) {
  df %>% 
    tidy() %>% 
    mutate_if(is.numeric,~round(., 3))
}

barGraph = function (data, outcome,group1,group2,title, xtitle,ytitle){
  dfc=summarySE(data, measurevar=outcome,
                groupvars=c(group1,group2), na.rm = T)
  dfc$high = dfc[,4]+dfc[,7]
  dfc$low = dfc[,4]-dfc[,7]
  pd <- position_dodge(0)
  ggplot(dfc, aes_string(x=group1, y=outcome, fill = group2)) +
      geom_bar(position=position_dodge(), stat="identity", colour="black" ) +
      labs(title="")+
      guides(fill=guide_legend(title=NULL))+
      theme_bw()+
      theme(plot.title = element_text(hjust=0.5,size = rel(1.5)),
            axis.title.y = element_text(face="bold",  size=14),
            axis.text.x  = element_text( vjust=0.5, size=18),
            axis.text.y  = element_text( vjust=0.5, size=12),
            axis.title.x = element_text( vjust=0.5, size=18)) +
    #coord_cartesian(ylim=c(3, 6)) +
    labs(title = title,
         x = xtitle, 
         y = ytitle)+
    geom_errorbar(aes(ymin=low, ymax=high),
                    width=.1,position=position_dodge(.9))
}

barGraph2 = function (data, outcome,group1,group2,title, xtitle,ytitle){
  dfc=summarySE(data, measurevar=outcome,
                groupvars=c(group1,group2), na.rm = T)
  dfc$high = dfc[,4]+dfc[,7]
  dfc$low = dfc[,4]-dfc[,7]
  pd <- position_dodge(0)
  ggplot(dfc, aes_string(x=group1, y=outcome, fill = group2)) +
      geom_bar(position=position_dodge(), stat="identity", colour="black" ) +
      labs(title="")+
      guides(fill=guide_legend(title=NULL))+
      theme_bw()+
      coord_cartesian(ylim = c(200, 225)) + 
      theme(plot.title = element_text(hjust=0.5,size = rel(1.5)),
            axis.title.y = element_text(face="bold",  size=14),
            axis.text.x  = element_text( vjust=0.5, size=18),
            axis.text.y  = element_text( vjust=0.5, size=12),
            axis.title.x = element_text( vjust=0.5, size=18)) +
    #coord_cartesian(ylim=c(3, 6)) +
    labs(title = title,
         x = xtitle, 
         y = ytitle)+
    geom_errorbar(aes(ymin=low, ymax=high),
                    width=.1,position=position_dodge(.9))
}

lineGraph = function (data, outcome,group1,group2,title, xtitle,ytitle){
  dfc=summarySE(data, measurevar=outcome,
                groupvars=c(group1,group2), na.rm = T)
  print(dfc)
  dfc$high = dfc[,4]+dfc[,7]
  dfc$low = dfc[,4]-dfc[,7]
  pd <- position_dodge(0)
  ggplot(dfc,aes_string(x=group2, y=outcome ,fill = group1, colour =group1))+
    geom_errorbar(aes(ymin=low, ymax=high), width=.1)+
    geom_line( aes_string(linetype= group1, group=group1),size = .5)+
    #facet_wrap(as.formula(paste("~", group1)),nrow=2)+
    geom_point()+
    theme_ipsum() +
    scale_color_manual(values=c("#69b3a2", "#404080")) +
    theme(plot.title = element_text(hjust=0.5,size = rel(1.5)),
          axis.title.y = element_text(size=14),
          axis.text.x  = element_text( vjust=0.5, size=14),
          axis.text.y  = element_text( vjust=0.5, size=12),
          axis.title.x = element_text( vjust=0.5, size=14)) +
    labs(title = title,
          x = xtitle, 
          y = ytitle)
}


# add age category
d = d %>%
  mutate(age = as.numeric(age)) %>%
  mutate(age_cat = case_when(
    (.$age<=31)==TRUE ~ "18-31",
    (.$age>31)==TRUE ~ "32_plus"))
d[,c("age", "age_cat")]

# add political category
d = d %>%
  mutate(political_ideology = as.factor(political_ideology)) %>%
  mutate(politic_cat = case_when(
    (.$political_ideology == "Slightly conservative" | .$political_ideology == "Moderately convservative" | .$political_ideology == "Strong conservative")==TRUE ~ "conservative",
    (.$political_ideology == "Slightly liberal" | .$political_ideology == "Moderate liberal" | .$political_ideology == "Strong liberal")==TRUE ~ "liberal",
    (.$political_ideology == "Neutral") == TRUE ~ "neutral"))
d[,c("political_ideology", "politic_cat")]

# how many participants in total
length(unique(d$participant_id))

# add the sign of agents' emotional rating
d = d %>%
  mutate(agent_rating_sign = ifelse(agent_rating >=0, "positive rating", "negative rating"))
d$agent_absRat = abs (d$agent_rating)
d$subject_absRat = abs (d$subject_rating)

# add two table of kept-only and eliminate-only agents
d_kept <- d %>% 
      filter(kept == 'kept')
d_eliminate <- d %>%
  filter(kept == 'eliminate')

# add columns of agent comments containing "lonely" and "popular"
d$agent_withlonely = ifelse(grepl("lone",d$agent_response), 1, 0)
d$agent_withpopular = ifelse(grepl("pop", d$agent_response), 1, 0)

# create popularity coefficient
r = glmer(kept ~ agent_liking + (agent_liking | participant_id), family = binomial, data = d)

d_coef <- coef(r)$participant_id

d_coef <- d_coef %>% 
  rownames_to_column(., "participant_id") %>% 
  dplyr::select(participant_id, agent_liking) %>% 
  dplyr::rename(per_person_kept = agent_liking)

p <- d_coef %>%
  ggplot( aes(x=per_person_kept)) +
    theme_bw()+
    geom_histogram( color="#e9ecef", alpha=0.6, , position="dodge") +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    #theme_ipsum() +
    labs(x = "Popularity coefficient", y = "Count") ;p

nm <- "popularity_coef"
d[nm] <- lapply(nm, function(x) d_coef[["per_person_kept"]][match(d$participant_id, d_coef$participant_id)])
```



### Descriptives
```{r Descriptives of demographics}

des = d %>%
  group_by(participant_id)%>%
  slice(1)

# age stats
mean(des$age)
sd(des$age)
range(des$age)
d_age = d %>%
  dplyr::select(participant_id, age, age_cat,gender) 
d_age = distinct(d_age)
ggplot(d_age, aes(x = `age`)) +
        geom_bar() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))

# gender stats
table(des$gender)
table(des$race_eth)
d_gender = d %>%
  dplyr::select(participant_id, age, age_cat,gender) 
d_gender = distinct(d_gender)
ggplot(d_gender, aes(x = `gender`)) +
        geom_bar() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))

# loneliness stats
ggplot(d, aes(y = .loneliness, color = lonely_cat, 
                     fill = lonely_cat, x = lonely_cat)) + geom_point(alpha = 0.3) + geom_jitter()
p <- des %>%
  ggplot( aes(x=.loneliness)) +
    theme_bw()+
    geom_histogram( color="#e9ecef", alpha=0.6, , position="dodge") +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    #theme_ipsum() +
    labs(x = "Lonelness", y = "Count") ;p
median (des$.loneliness)
table(des$lonely_cat)


sd(des$popularity_ratingappealing)
```



### H1 Analysis (Are lonely individuals more attracted to popular others)

#### homophily
```{r homophily}
r = lmer(rating_dist ~ kept + (1|participant_id), data = d); summary(r)
# significant - people tend to choose peers who rate artworks more similarly

```

#### homophily & loneliness
```{r homophily and loneliness}
r = glmer(kept ~ rating_dist*.loneliness + (1|participant_id), family = "binomial",data = d); summary(r)
barGraph (d, "rating_dist","lonely_cat","kept","homophily & loneliness", "","rating distance")
```

#### popularity
```{r popularity}
r = glmer(kept ~ agent_liking + (1|participant_id),family = binomial, data = d); summary(r)
r.squaredGLMM(r)
confint(r)
# graph
lineGraph  (d, "agent_liking","kept","trial","popularity effect", "trials","popularity")
p<-ggplot(data=d, aes(x=kept, y=agent_liking)) +
  geom_bar(stat="identity", fill="steelblue")+
  coord_cartesian(ylim = c(2700000, 2800000)) + 
  theme_minimal()
p+ xlab(" ") + ylab("popularity")
```

#### popularity and loneliness (H1)
```{r popularity_loneliness}
r = glmer(kept ~ agent_liking*.loneliness + (1|participant_id), family = "binomial",data = d); summary(r)

# significant - the more lonely people are, the more they tend to keep popular peers
r.squaredGLMM(r)
# graph
barGraph  (d, "agent_liking","lonely_cat","kept","popularity & loneliness", "","popularity")

#library(hrbrthemes)
lineGraph (d, "agent_liking","lonely_cat","kept","", "Participant Loneliness","Peer Popularity")
```

### Exploratory Analysis
#### within trial effects 
```{r setting up within trial effects }
s=d%>%
  filter(kept =="kept")%>%
  #filter(trial <4) %>%
  dplyr::select(participant_id,
         trial, 
         agents_names,
         agent_rating,
         kept, 
         kept_1_response_liking, 
         kept_2_response_liking, kept_3_response_liking,subject_rating, lonely_cat, agent_liking, rating_dist)%>%
  dplyr::group_by(participant_id,trial)%>%
  #mutate(agentNumber = seq(1:3)) %>%
  ungroup()%>%
  dplyr::group_by(participant_id)%>%#, agentNumber)%>%
  arrange(participant_id,trial)


s = s %>%
  #mutate(like_repeat = ifelse(kept_1_response_liking == kept_2_response_liking | kept_1_response_liking == kept_3_response_liking | kept_3_response_liking == kept_2_response_liking, 1,0))%>%
  dplyr::mutate(kept_order = ifelse(agent_liking == kept_1_response_liking, 1, ifelse(agent_liking == kept_2_response_liking, 2,3)))%>%
  dplyr::mutate(kept_order = as.factor(kept_order))

p <- ggplot(s, aes(y = agent_liking, x = trial, color = kept_order)) +
  #geom_point(alpha=0.4) +
  geom_smooth(method='auto')+ 
  facet_wrap(~lonely_cat)+
    theme_bw()+
    theme(plot.title = element_text(hjust=0.5,size = rel(1.5)),
          axis.title.y = element_text(face="bold",  size=14),
          axis.text.x  = element_text( vjust=0.5, size=12),
          axis.text.y  = element_text( vjust=0.5, size=12),
          axis.title.x = element_text( vjust=0.5, size=18)) +
  xlab("Trial") + ylab("Popularity"); p

barGraph2(s, "agent_liking","kept_order","lonely_cat","within trial", "","popularity")
```

#### correlation between loneliness and other measures

##### lonelinss & my impression of the agent who has more average likes
```{r loneliness and popular agent}
d_moderate = d %>%
  dplyr::select(.loneliness, pop_agent_popularity, pop_agent_positivity, pop_agent_interesting, pop_agent_like, pop_agent_ratingsimilar, pop_agent_likesimilar)
d_moderate = distinct(d_moderate)
d_cor = rcorr(as.matrix(d_moderate), type=c("pearson"))
a = corrplot(d_cor$r, tl.cex = 0.8, order = "alphabet",p.mat=d_cor$P, insig="blank", method = "color", diag = FALSE, type = "upper",number.cex = 0.8,
         addCoef.col = "black", # Add coefficient of correlation 
         tl.col="black")  # Text label color and rotation
```

##### lonelinss & my impression of the agent who has less average likes
```{r loneliness and non-popular agent}
d_moderate = d %>%
  dplyr::select(.loneliness, nonpop_agent_popularity, nonpop_agent_positivity, nonpop_agent_interesting, nonpop_agent_like, nonpop_agent_ratingsimilar, nonpop_agent_likesimilar)
d_moderate = distinct(d_moderate)
d_cor = rcorr(as.matrix(d_moderate), type=c("pearson"))
b = corrplot(d_cor$r, tl.cex = 0.8, order = "alphabet",p.mat=d_cor$P, insig="blank", method = "color", diag = FALSE, type = "upper",number.cex = 0.8,
         addCoef.col = "black", # Add coefficient of correlation 
         tl.col="black")  # Text label color and rotation

```

##### loneliness & do I see myself as popular
```{r loneliness and self perception}
d_moderate = d %>%
  dplyr::select(.loneliness, popularity_selfpopular, popularity_attractpopular, popularity_interetpopular, popularity_wishpopular, popularity_commentpopular, popularity_commentinteresting, popularity_ratingappealing)
d_moderate = distinct(d_moderate)
d_cor = rcorr(as.matrix(d_moderate), type=c("pearson"))
corrplot(d_cor$r, tl.cex = 0.8, order = "alphabet",p.mat=d_cor$P, insig="blank", method = "color", diag = FALSE, type = "upper",number.cex = 0.8,
         addCoef.col = "black", # Add coefficient of correlation 
         tl.col="black")  # Text label color and rotation
```

##### attraction to popularity & do I see myself as popular
```{r attration to popularity and self perception}
popularity_cor = d %>%
  dplyr::select(popularity_coef, popularity_selfpopular, popularity_attractpopular, popularity_interetpopular, popularity_wishpopular, popularity_commentpopular, popularity_commentinteresting, popularity_ratingappealing)
d_cor = rcorr(as.matrix(popularity_cor), type=c("pearson"))
corrplot(d_cor$r, tl.cex = 0.8, order = "alphabet",p.mat=d_cor$P, insig="blank", method = "color", diag = FALSE, type = "upper",number.cex = 0.8,
         addCoef.col = "black", # Add coefficient of correlation 
         tl.col="black")  # Text label color and rotation
```

##### attraction to popularity & my impression of the agent who has more average likes
```{r attraction to popularity and popular agent}
popularity_cor = d %>%
  dplyr::select(popularity_coef, pop_agent_popularity, pop_agent_positivity, pop_agent_interesting, pop_agent_like, pop_agent_ratingsimilar, pop_agent_likesimilar)
d_cor = rcorr(as.matrix(popularity_cor), type=c("pearson"))
corrplot(d_cor$r, tl.cex = 0.8, order = "alphabet",p.mat=d_cor$P, insig="blank", method = "color", diag = FALSE, type = "upper",number.cex = 0.8,
         addCoef.col = "black", # Add coefficient of correlation 
         tl.col="black")  # Text label color and rotation
```

##### attraction to popularity & my impression of the agent who has less average likes
```{r attraction to popularity and non-popular agent}
popularity_cor = d %>%
  dplyr::select(popularity_coef, nonpop_agent_popularity, nonpop_agent_positivity, nonpop_agent_interesting, nonpop_agent_like, nonpop_agent_ratingsimilar, nonpop_agent_likesimilar)
d_cor = rcorr(as.matrix(popularity_cor), type=c("pearson"))
corrplot(d_cor$r, tl.cex = 0.8, order = "alphabet",p.mat=d_cor$P, insig="blank", method = "color", diag = FALSE, type = "upper",number.cex = 0.8,
         addCoef.col = "black", # Add coefficient of correlation 
         tl.col="black")  # Text label color and rotation
```

##### combined correlation
```{r combined correlation}
# general correlation
d_moderate = d %>%
  dplyr::select(.loneliness, popularity_coef, pop_agent_popularity, pop_agent_positivity, pop_agent_interesting, pop_agent_like, pop_agent_ratingsimilar, pop_agent_likesimilar, nonpop_agent_popularity, nonpop_agent_positivity, nonpop_agent_interesting, nonpop_agent_like, nonpop_agent_ratingsimilar, nonpop_agent_likesimilar, popularity_selfpopular, popularity_attractpopular, popularity_interetpopular, popularity_wishpopular, popularity_commentpopular, popularity_commentinteresting, popularity_ratingappealing)
d_moderate = distinct(d_moderate)
d_cor = rcorr(as.matrix(d_moderate), type=c("pearson"))
format_cor = function(cor, p) {
  stars = ifelse(p < 0.001, "***", ifelse(p < 0.01, "**", ifelse(p < 0.05, "*", "")))
  formatted = sprintf("%.2f%s", cor, stars)
  formatted[formatted == "1.00"] = ""  # Remove diagonal
  return(formatted)
}
cor_matrix = matrix(format_cor(d_cor$r, d_cor$P), nrow=21)
colnames(cor_matrix) = rownames(cor_matrix) = colnames(d_moderate)
cor_table = as.data.frame(cor_matrix)
cor_table = cbind(Variable = rownames(cor_table), cor_table)
kable(cor_table, format = "markdown", caption = "Correlation Matrix", align = 'c')
#write.csv(cor_table, "correlation_table.csv", row.names = FALSE)

means = sapply(d_moderate, mean, na.rm = TRUE)
sds = sapply(d_moderate, sd, na.rm = TRUE)

# Add means and SDs to the correlation table
cor_table = cor_table %>%
  dplyr::mutate(
    Variable = rownames(cor_table),
    Mean = sprintf("%.2f", means),
    SD = sprintf("%.2f", sds)
  ) %>%
  dplyr::select(Variable, Mean, SD, everything())

# Save as CSV
#write.csv(cor_table, "correlation_table_with_means_sds.csv", row.names = FALSE)
```

#### mediation analysis
```{r}

# List of mediators
mediators <- c(
  "popularity_selfpopular", 
  "popularity_commentpopular", 
  "popularity_commentinteresting",
  "popularity_wishpopular", 
  "pop_agent_ratingsimilar", 
  "pop_agent_likesimilar"
)
med_model <- lm(popularity_selfpopular ~ .loneliness, data = d)
# Fit the outcome model
out_model <- lm(popularity_coef ~ .loneliness + popularity_selfpopular, data = d)
# Run the mediation analysis with bootstrapping
med_result <- mediate(med_model, out_model, treat = ".loneliness", mediator = "popularity_selfpopular", boot = TRUE, sims = 5000)
summary(med_result)

med_model <- lm(pop_agent_ratingsimilar ~ .loneliness, data = d)
# Fit the outcome model
out_model <- lm(popularity_coef ~ .loneliness + pop_agent_ratingsimilar, data = d)
# Run the mediation analysis with bootstrapping
med_result <- mediate(med_model, out_model, treat = ".loneliness", mediator = "pop_agent_ratingsimilar", boot = TRUE, sims = 5000)
summary(med_result)

med_model <- lm(pop_agent_likesimilar ~ .loneliness, data = d)
# Fit the outcome model
out_model <- lm(popularity_coef ~ .loneliness + pop_agent_likesimilar, data = d)
# Run the mediation analysis with bootstrapping
med_result <- mediate(med_model, out_model, treat = ".loneliness", mediator = "pop_agent_likesimilar", boot = TRUE, sims = 5000)
summary(med_result)

med_model <- lm(nonpop_agent_ratingsimilar ~ .loneliness, data = d)
# Fit the outcome model
out_model <- lm(popularity_coef ~ .loneliness + nonpop_agent_ratingsimilar, data = d)
# Run the mediation analysis with bootstrapping
med_result <- mediate(med_model, out_model, treat = ".loneliness", mediator = "nonpop_agent_ratingsimilar", boot = TRUE, sims = 5000)
summary(med_result)

med_model <- lm(nonpop_agent_likesimilar ~ .loneliness, data = d)
# Fit the outcome model
out_model <- lm(popularity_coef ~ .loneliness + nonpop_agent_likesimilar, data = d)
# Run the mediation analysis with bootstrapping
med_result <- mediate(med_model, out_model, treat = ".loneliness", mediator = "nonpop_agent_likesimilar", boot = TRUE, sims = 5000)
summary(med_result)

med_model <- lm(popularity_wishpopular ~ .loneliness, data = d)
# Fit the outcome model
out_model <- lm(popularity_coef ~ .loneliness + popularity_wishpopular, data = d)
# Run the mediation analysis with bootstrapping
med_result <- mediate(med_model, out_model, treat = ".loneliness", mediator = "popularity_wishpopular", boot = TRUE, sims = 5000)
summary(med_result)
```


##### attractive to popularity coefficient & do i see myself as popular
```{r}
## lonely & attractive to popularity coefficient & do i see myself as popular
r = lmer(popularity_coef ~ popularity_selfpopular * .loneliness + (1|participant_id), data = d); summary(r)
r = lmer(popularity_coef ~ .loneliness * popularity_selfpopular + (1|participant_id), data = d); summary(r)
# SIG
lineGraph (d, "popularity_coef","lonely_cat","popularity_selfpopular","", "How much do I see myself as popular", "Coefficient of attractiveness to popularity")
ggplot(d, aes(x = popularity_selfpopular, y = popularity_coef, color = lonely_cat, fill = lonely_cat))+ 
  geom_point(alpha = 0.3) + 
  geom_smooth(method=lm, se=FALSE) 
```

##### attractive to popularity coefficient & to what extent are you interested in popular people
```{r}
r = lmer(popularity_coef ~ popularity_interetpopular + (1|participant_id), data = d); summary(r)
# SIG
ggplot(d, aes(x = popularity_interetpopular, y = popularity_coef)) + 
  geom_point(alpha = 0.7) + 
  geom_smooth(method=lm, se=FALSE) 

## lonely
r = lmer(popularity_coef ~ popularity_interetpopular * .loneliness + (1|participant_id), data = d); summary(r)
# SIG
lineGraph (d, "popularity_coef","lonely_cat","popularity_interetpopular","", "Am I interested in popular people", "Coefficient of attractiveness to popularity")
ggplot(d, aes(x = popularity_interetpopular, y = popularity_coef, color = lonely_cat, fill = lonely_cat))+ 
  geom_point(alpha = 0.3) + 
  geom_smooth(method=lm, se=FALSE) 
```