---
title: "Popularity and Loneliness Study 1 Data Analysis"
output: html_notebook
---

We use groundhog (https://groundhogr.com/) to manage our packages. Groundhog makes sure that our package versions are consistent with the current date. This way, everyone will be using packages from the same date to prevent any issues related to package versioning in future analyses. 

To use groundhog, please: 
(1) make sure that you have the latest version of R/ RStudio installed; 
(2) install RTools
(3) make sure you are in a new R Session


The R Version used to create this file is: `R version 4.3.0 (2023-04-21 ucrt)`. You can change this out with your own version of R if you are using this template to create your own analysis. If you are reproducing another person's analysis, please download the version of R used by the previous person to ensure a proper reproduction of the code.

You can identify your version of R by typing `version` into the R Console

You can switch your R version by pressing `Tools` > `Global Options` > `R Version`


```{r download packages and format csv to prepare for analysis}

library("groundhog")



# put all packages in and call groundhog
pkgs <- c("tidyverse", 'Rmisc', 'tidyverse', 'hablar',
               'patchwork', 'network', 'cowplot', # figures
               'effectsize', 'parameters', 'performance', 'lmerTest', # regression models
               'lsa','interactions', # cosine
               'MuMIn','hrbrthemes', "patchwork",'dplyr'
    )

pkgs_all <- c(pkgs)

# call groundhog. Change out the date for today's date (unless you are running an old analysis)
groundhog.library(pkgs_all, "2025-04-09")
```


### Descriptives
```{r Descriptives of experiment results}
# Get original datasets for supplementary information
data = read.csv('../data/raw/processed_data.csv')
trait <- read.csv('../data/raw/df.traitNet_transformed_fa19sp20.csv', header = T)

# Create a dataframe with unique participants from data
unique_pids <- unique(data$ego)
results <- data.frame(PID = unique_pids)

# Extract gender information from trait dataset
results$gender_fa19 <- NA
results$gender_sp20 <- NA

for (i in 1:nrow(results)) {
  pid <- results$PID[i]
  
  # Extract gender from trait data 
  gender_fa19_row <- trait$gender_fa19[trait$PID == pid]
  gender_sp20_row <- trait$gender_sp20[trait$PID == pid]
  
  if (length(gender_fa19_row) > 0 && !is.na(gender_fa19_row[1])) {
    results$gender_fa19[i] <- gender_fa19_row[1]
  }
  
  if (length(gender_sp20_row) > 0 && !is.na(gender_sp20_row[1])) {
    results$gender_sp20[i] <- gender_sp20_row[1]
  }
}

# Combine gender data (preferring fa19, but using sp20 if fa19 is NA)
results$gender <- ifelse(!is.na(results$gender_fa19), 
                         results$gender_fa19, 
                         results$gender_sp20)

# Count and display gender information
gender_counts <- table(results$gender, useNA = "ifany")
gender_percent <- round(100 * gender_counts / sum(gender_counts), 1)

cat("Gender Distribution:\n")
print(gender_counts)
cat("\nGender Percentages:\n")
print(gender_percent)

# Age statistics
age_fa19 <- trait$age_fa19[trait$PID %in% unique_pids]
age_stats <- c(
  Mean = mean(age_fa19, na.rm = TRUE),
  SD = sd(age_fa19, na.rm = TRUE),
  Min = min(age_fa19, na.rm = TRUE),
  Max = max(age_fa19, na.rm = TRUE),
  Missing = sum(is.na(age_fa19))
)

cat("\nAge Statistics (Fall 2019):\n")
print(age_stats)

# Race information from trait dataset
results$race_fa19 <- NA
results$race_sp20 <- NA

for (i in 1:nrow(results)) {
  pid <- results$PID[i]
  
  race_fa19_row <- trait$race_clean_fa19[trait$PID == pid]
  race_sp20_row <- trait$race_clean_sp20[trait$PID == pid]
  
  if (length(race_fa19_row) > 0 && !is.na(race_fa19_row[1])) {
    results$race_fa19[i] <- race_fa19_row[1]
  }
  
  if (length(race_sp20_row) > 0 && !is.na(race_sp20_row[1])) {
    results$race_sp20[i] <- race_sp20_row[1]
  }
}

# Combine race data
results$race <- ifelse(!is.na(results$race_fa19), 
                       results$race_fa19, 
                       results$race_sp20)

# Count and display race information
race_counts <- table(results$race, useNA = "ifany")
race_percent <- round(100 * race_counts / sum(race_counts), 1)

race_df <- data.frame(
  Race = names(race_counts),
  Count = as.integer(race_counts),
  Percentage = as.numeric(race_percent)
)

cat("\nRace Distribution:\n")
print(race_df)

# Network nominations from the data dataset
# First, convert term to character if it's a factor
data_term <- if(is.factor(data$Term)) as.character(data$Term) else data$Term

# Count nominations by participant and term
nominations_per_pid <- data %>%
  group_by(ego, Term) %>%
  dplyr::summarise(num_nominations = n(), .groups = "drop")

# Basic statistics for nominations
avg_nominations_by_term <- nominations_per_pid %>%
  group_by(Term) %>%
  dplyr::summarise(
    avg_nominations = mean(num_nominations),
    median_nominations = median(num_nominations),
    sd_nominations = sd(num_nominations),
    min_nominations = min(num_nominations),
    max_nominations = max(num_nominations),
    total_pids = n()
  )

cat("\nNomination Statistics by Term:\n")
print(avg_nominations_by_term)

# Additional participant statistics
cat("\nParticipant Summary:\n")
cat("Total unique participants:", length(unique_pids), "\n")

# Get participants by term
fall_pids <- unique(data$ego[data$Term == "Fall 2019" | data$Term == "fa19"])
spring_pids <- unique(data$ego[data$Term == "Spring 2020" | data$Term == "sp20"])

both_terms <- intersect(fall_pids, spring_pids)
fall_only <- setdiff(fall_pids, spring_pids)
spring_only <- setdiff(spring_pids, fall_pids)

cat("Participants in Fall 2019 only:", length(fall_only), 
    sprintf("(%.1f%%)", 100 * length(fall_only) / length(unique_pids)), "\n")
cat("Participants in Spring 2020 only:", length(spring_only), 
    sprintf("(%.1f%%)", 100 * length(spring_only) / length(unique_pids)), "\n")
cat("Participants in both terms:", length(both_terms), 
    sprintf("(%.1f%%)", 100 * length(both_terms) / length(unique_pids)), "\n")

# Loneliness measures from data dataset
# Note: Handle the case where term might be a factor or character
fall_data <- data[data$Term == "Fall 2019" | data$Term == "fa19",]
spring_data <- data[data$Term == "Spring 2020" | data$Term == "sp20",]

# Get unique loneliness values per participant (avoid duplicates from multiple nominations)
lone_fa19 <- sapply(unique(fall_data$ego), function(pid) {
  # Get the first non-NA loneliness value for this participant
  lone_vals <- fall_data$loneEgo[fall_data$ego == pid]
  if(length(lone_vals) > 0) return(lone_vals[1])
  return(NA)
})

lone_sp20 <- sapply(unique(spring_data$ego), function(pid) {
  # Get the first non-NA loneliness value for this participant
  lone_vals <- spring_data$loneEgo[spring_data$ego == pid]
  if(length(lone_vals) > 0) return(lone_vals[1])
  return(NA)
})

lone_stats <- data.frame(
  Term = c("Fall 2019", "Spring 2020"),
  Mean = c(mean(lone_fa19, na.rm = TRUE), mean(lone_sp20, na.rm = TRUE)),
  SD = c(sd(lone_fa19, na.rm = TRUE), sd(lone_sp20, na.rm = TRUE)),
  Median = c(median(lone_fa19, na.rm = TRUE), median(lone_sp20, na.rm = TRUE)),
  Min = c(min(lone_fa19, na.rm = TRUE), min(lone_sp20, na.rm = TRUE)),
  Max = c(max(lone_fa19, na.rm = TRUE), max(lone_sp20, na.rm = TRUE)),
  Missing = c(sum(is.na(lone_fa19)), sum(is.na(lone_sp20)))
)

cat("\nLoneliness Statistics (Z-scores):\n")
print(lone_stats)

# Calculate popularity as in-degree (number of nominations received) for each participant
# by counting how many times they appear as an alter
popularity_data <- data %>%
  group_by(Term, alter) %>%
  dplyr::summarise(indegree = n(), .groups = "drop") 

# Calculate statistics by term
popularity_stats <- popularity_data %>%
  group_by(Term) %>%
  dplyr::summarise(
    mean_indegree = mean(indegree, na.rm = TRUE),
    sd_indegree = sd(indegree, na.rm = TRUE),
    median_indegree = median(indegree, na.rm = TRUE),
    min_indegree = min(indegree, na.rm = TRUE),
    max_indegree = max(indegree, na.rm = TRUE),
    n = n()
  )

# Print the results
cat("Popularity Statistics (Indegree):\n")
print(popularity_stats)

data <- data %>%
  left_join(popularity_data, by = c("Term" = "Term", "alter" = "alter"))

data <- data %>%
  dplyr::rename(alter_popularity = indegree)
```

```{r descriptive stats graphs}
data %>% 
  group_by(Term, ego) %>% 
  slice(1) %>% ungroup %>% 
  # FIGURE SYNTAX #
  ggplot(aes(x = loneBinEgo, 
             label = ..count.., fill = Term)) +
  geom_histogram(stat='count',color="#e9ecef", alpha=0.6, position = 'identity', binwidth = 0.5) + 
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  geom_text(stat='count', vjust = -0.5) + 
  ylim(0, 700) + 
  theme_linedraw() + theme(plot.title = element_text(face = "bold")) +
  labs(x = 'Loneliness Status',
       y = 'Count',
       title = "B",
       subtitle = "Numbers of Lonely VS. Not Lonely Egos")


ggplot(data, aes(x = loneEgo, fill = Term)) +
    geom_histogram(color="#e9ecef", 
                  alpha=0.6,
                  position = position_dodge(width = 0.8),  # Changed to dodged position
                  binwidth = 0.5) + 
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    theme_linedraw() + 
    labs(x = "Ego's loneliness", 
         y = "Count", 
         title = "Distribution of Ego's Loneliness") + 
    theme(plot.title = element_text(face = "bold"))

# Distribution of Ego's Nominations (Outdegree)
# Calculate nominations (outdegree) per participant
nominations_count <- data %>%
  group_by(ego, Term) %>%
  dplyr::summarise(n = n(), .groups = "drop")

# Plot distribution of ego's nominations (outdegree)
p <- nominations_count %>%
  ggplot(aes(x=n, fill=Term)) +
    geom_histogram(color="#e9ecef", alpha=0.6, position = 'identity', binwidth = 0.5) +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    # Add separate mean lines for each term
    geom_vline(data = nominations_count %>% 
                 dplyr::group_by(Term) %>% 
                 dplyr::summarise(mean_n = mean(n, na.rm=TRUE)),
               aes(xintercept=mean_n, color=Term), 
               linetype = "dashed", size=1) +
    scale_color_manual(values=c("#216843", "#202060")) +
    theme_linedraw() +
    labs(x = "Outdegree - Ego's nomination count", 
         y = "Frequency", 
         title = "A", 
         subtitle = "Distribution of Ego's Nominations") + 
    theme(plot.title = element_text(face = "bold"),
          legend.position = "top",
          legend.title = element_blank()) +
    # Set better x-axis limits
    xlim(0, max(nominations_count$n) + 1)

# Distribution of Alter's Popularity (Indegree)
unique_popularity <- data %>%
  select(Term, alter, alter_popularity) %>%
  distinct()

# Plot distribution of alter's popularity (indegree)
q <- data %>%
  filter(!is.na(alter_popularity)) %>%
  ggplot(aes(x=alter_popularity, fill=Term)) +
    geom_histogram(color="#e9ecef", alpha=0.6, position = 'identity', binwidth = 0.5) +
    scale_fill_manual(values=c("#69b3a2", "#404080")) +
    # Add separate mean lines for each Term
    geom_vline(data = unique_popularity  %>% 
                 filter(!is.na(alter_popularity)) %>%
                 dplyr::group_by(Term) %>% 
                 dplyr::summarise(mean = mean(alter_popularity, na.rm=TRUE)),
               aes(xintercept=mean, color=Term), 
               linetype = "dashed", size=1) +
    scale_color_manual(values=c("#216843", "#202060")) +
    theme_linedraw() +
    labs(x = "Indegree - Alter's popularity", 
         y = "Frequency", 
         title = "B", 
         subtitle = "Distribution of Alter's Popularity") + 
    theme(plot.title = element_text(face = "bold"),
          legend.position = "top",
          legend.title = element_blank())

# Combine both plots with patchwork
combined_plot <- p + q + 
  plot_layout(guides = "collect") &  # Collect legends
  theme(legend.position = "bottom")  # Position legend at bottom

# Display the combined plot
combined_plot
```


### H1 Analysis: Do lonely egos tend to nominate more popular alters? 
```{r H1}
# alter indegree as estimation of popularity
data$log_alter_received_nominations <- log1p(data$alter_popularity)

r <- lmer(log_alter_received_nominations ~ loneEgo + inEgo + (1|ego), data = data); summary(r)
r.squaredGLMM(r)
confint(r)

p <- ggplot(data, aes(y = log_alter_received_nominations, x = loneEgo, color = Term)) +
  #geom_point(alpha=0.4) +
  geom_smooth(method = "lm", fill = "lightgray") + 
    theme_ipsum() +
    #facet_wrap(~Term) +
    theme(plot.title = element_text(hjust=0.5,size = rel(1.5)),
          axis.title.y = element_text(size=14),
          axis.text.x  = element_text( vjust=0.5, size=12),
          axis.text.y  = element_text( vjust=0.5, size=12),
          axis.title.x = element_text(vjust=0.5, size=14)) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
  xlab("Ego's loneliness") + ylab("Alter's popularity"); p



# Create a clean dataset for plotting
plot_data <- data %>%
  filter(!is.na(loneEgo) & !is.na(inEgo) & !is.na(log_alter_received_nominations))

# Create partial regression plot by removing the effect of inEgo
# First, get residuals after controlling for inEgo
lm_x <- lm(loneEgo ~ inEgo, data = plot_data)
lm_y <- lm(log_alter_received_nominations ~ inEgo, data = plot_data)

plot_data$loneEgo_resid <- residuals(lm_x)
plot_data$popularity_resid <- residuals(lm_y)

p <- ggplot(plot_data, aes(y = popularity_resid, x = loneEgo_resid, color = Term)) +
  geom_smooth(method = "lm", fill = "lightgray") + 
  theme_ipsum() +
  theme(plot.title = element_text(hjust=0.5,size = rel(1.5)),
        axis.title.y = element_text(size=14),
        axis.text.x  = element_text( vjust=0.5, size=12),
        axis.text.y  = element_text( vjust=0.5, size=12),
        axis.title.x = element_text(vjust=0.5, size=14)) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
  xlab("Ego's loneliness (residualized)") + 
  ylab("Alter's popularity (residualized)")

p
```

### Exploratory Analysis
#### whether lonely people were less likely to be nominated in general & reciprocity
```{r exploratory loneliness being nominated}
indegree_counts <- data %>%
  dplyr::group_by(Term, alter) %>%
  dplyr::summarise(indegree = n(), .groups = "drop")
data <- data %>%
  left_join(indegree_counts, by = c("Term", "alter"))

fit <- lmer(indegree ~ loneAlter + (1|alter), data = data); summary(fit)
r.squaredGLMM(fit)
confint(fit)

fit <- lmer(recpPer ~ loneEgo + (1|ego), data); summary(fit)
r.squaredGLMM(fit)
confint(fit)

a <- ggplot(data, aes(y = indegree, x = loneAlter, color = Term)) +
    geom_smooth(method = "lm", fill = "lightgray") + 
    scale_color_manual(values=c("#69b3a2", "#404080")) +
    theme_linedraw() +
    labs (x = "Loneliness", y = "Received Nominations", title = "A", subtitle = "Received Nominations & Loneliness") + theme(plot.title = element_text(face = "bold"))

b <- ggplot(data, aes(y = recpPer, x = loneEgo, color = Term)) +
  #geom_point(alpha=0.4) +
  geom_smooth(method='lm', fill = "lightgray")+ 
    theme_linedraw()+
  scale_color_manual(values=c("#69b3a2", "#404080")) +
  labs (x = "Loneliness", y = "Reciprocity", title = "B", subtitle = "Reciprocity & Loneliness") + theme(plot.title = element_text(face = "bold"))
a + b
```


#### whether lonely people are reciprocated more or less by popular people.
```{r exploratory loneliness reciprocity}
fit <- lmer(recpPer ~ loneEgo* log_alter_received_nominations + (1|ego), data); summary(fit)
r.squaredGLMM(fit)
confint(fit)

# people might APPEAR not to reciprocate nominations, because the max # they can make is fixed (at 6 or 8 depending on the survey year).  So they might actually be friends with people they can’t nominate. 
# here we calculate the nomination saturation of popular people

# Step 1: Calculate outdegree for each alter (when they act as an ego)
# This counts how many nominations each person made when they were an ego
alter_as_ego <- data %>%
  filter(alter %in% unique(data$ego)) %>%  # Only include alters who are also egos
  select(Term, alter) %>%
  distinct() %>%
  dplyr::rename(ego_temp = alter)

outdegree_counts <- data %>%
  dplyr::group_by(Term, ego) %>%
  dplyr::summarise(outdegree = n(), .groups = "drop")

# Step 2: Join the outdegree counts to get each alter's outdegree
# (when they were acting as an ego)
alter_outdegree <- alter_as_ego %>%
  left_join(outdegree_counts, by = c("Term" = "Term", "ego_temp" = "ego")) %>%
  dplyr::rename(alter = ego_temp)

# Step 3: Calculate saturation rate (assuming max nominations = 6)
alter_saturation <- alter_outdegree %>%
  mutate(
    saturation_rate = outdegree / 6,
    is_saturated = (outdegree >= 6)  # TRUE if they used all 6 slots
  )

# Step 4: Join saturation information back to the main data
data_with_saturation <- data %>%
  left_join(alter_saturation %>% select(Term, alter, saturation_rate, is_saturated), 
            by = c("Term", "alter"))

# Step 5: Check if popular alters are more saturated
popular_saturation <- data_with_saturation %>%
  # Use alter_popularity to determine if alter is popular (above median)
  dplyr::group_by(Term) %>%
  dplyr::mutate(is_popular = alter_popularity > median(alter_popularity, na.rm = TRUE)) %>%
  ungroup() %>%
  # Check saturation rates by popularity
  group_by(Term, is_popular) %>%
  dplyr::summarise(
    mean_saturation = mean(saturation_rate, na.rm = TRUE),
    pct_saturated = mean(is_saturated, na.rm = TRUE) * 100,
    count = n(),
    .groups = "drop"
  )

# Print results
print(popular_saturation)
```

#### whether popular people were more likely to be nominated by lonely people in earlier nominations compared to later ones
```{r exploratory rank order}
network <- read.csv('../data/raw/edgeList_allNetworks.csv', header = T) %>%
  dplyr::filter(networkType=='CloseFrds') %>%
  dplyr::rename(ego = "PID", alter = "nom") %>%
  dplyr::select(-networkType) %>%
  dplyr::group_by(ego) %>%
  dplyr::mutate(rank = rank(rank, na.last = "keep")) %>%
  ungroup()
data2 = merge(network, data, by = c("ego", "alter"))

r = lmer(log_alter_received_nominations ~ rank + (1|ego), data = data2); summary(r)
r.squaredGLMM(r)
confint(r)

r = lmer(log_alter_received_nominations ~ rank*loneEgo + (1|ego), data = data2); summary(r)
r.squaredGLMM(r)
confint(r)
```